---
title: "Bangladesh surveillance greyspots"
author: "Elonia"
output: 
  pdf_document:
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE, eval=TRUE}
options(tinytex.verbose = TRUE)
knitr::opts_chunk$set(echo = FALSE, cache=FALSE, warning=FALSE, message=FALSE, fig.align="center")
library(kableExtra)

```

```{r captioner, include=FALSE, eval=TRUE}
library(captioner)
tab_nums <- captioner(prefix = "Table ", auto_space = FALSE)
fig_nums <- captioner(prefix = "Figure ", auto_space = FALSE)
```

```{r, settings}
source("source/util.R")
reload_source()

```

## Notes
The goal of this study is to identify how well the Bangladesh national cholera surveillance system captures:
1. the Bangladeshi population
1. the Bangladeshi population living in high, medium, and low risk cholera areas

We define cholera surveillance zones as geographies surrounding one of the 22 cholera sentinel hospitals. Surveillance zones are defined as the area enclosed within a circular buffer with a radius of 10 km, 30 km, or 50 km surrounding the coordinates of a given sentinel hospital.

The values we want to estimate include:
1. percentage of the population living in cholera surveillance zones
1. number and percentage of infections residing in cholera surveillance zones within the last year
1. number and percentage of infections residing in cholera surveillance zones that are in high, medium, and low infection risk areas
1. number and percentage of people living in high, medium, and low infection risk areas that would be captured by cholera surveillance zones

We use the following threshold for defining high, medium, and low risk infection areas:
* RR >= 1.5 is high risk
* 0.5 < RR < 1.5 is medium risk
* RR <= 0.5 is low risk

```{r, import-data, include = FALSE}

## sentinel hospital location data
hosp_dat <- read_csv("data/hosp_GPS.csv")

## WorldPop population raster (log-linear interpolation for 2015 from all WorldPop raster data )
pop_rast <- raster("data/BGD_ppp_2015_adj_v2.tif")
## shapefiles for Bangladesh
adm0_shp <- readRDS("data/BGD_adm0.rds")
adm2_shp <- readRDS("data/BGD_adm2.rds")

## import buffer files (multipolygon versions)
buff10_mp <- st_read("generated_data/buff_sf_multipoly_10km.shp")
buff30_mp <- st_read("generated_data/buff_sf_multipoly_30km.shp")
buff50_mp <- st_read("generated_data/buff_sf_multipoly_50km.shp")

## import buffer files (single polygon versions)
buff10_sp <- st_read("generated_data/buff_sf_singlepoly_10km.shp")
buff30_sp <- st_read("generated_data/buff_sf_singlepoly_30km.shp")
buff50_sp <- st_read("generated_data/buff_sf_singlepoly_50km.shp")

```


There are 22 sentinel hospital sites (`r tab_nums("tab-hospnames", display = "cite")`).

```{r, proc-tab-hospnames}

display_hospnames_tab <- hosp_dat %>% 
  dplyr::select(HOSP, Name, Division, LAT, LON)

tab_nums(name = "tab-hospnames", caption = "**Sentinel hospital IDs and locations.**", display = FALSE)
```

`r tab_nums("tab-hospnames", display = "full")`

```{r, disp-tab-hospnames}
knitr::kable(display_hospnames_tab, format = "pandoc", booktabs = T, align = "c", row.names = FALSE, col.names = c("ID", "Hospital", "Division", "Latitude", "Longitude"))

```

We defined 3 versions of basic hospital population catchment areas with 10 km, 30 km, and 50 km radial buffers (`r tab_nums("tab-hosp", display = "cite")`).


```{r, proc-tab-hosp}

display_hosp_tab <- hosp_dat %>%
  dplyr::mutate(HOSP = as.character(HOSP)) %>%
  dplyr::mutate(pop_buff10 = buff10_sp$pop, pop_buff30 = buff30_sp$pop, pop_buff50 = buff50_sp$pop) %>%
  dplyr::select(HOSP, contains("buff"))

#tot_row <- data.frame(HOSP = "Total", pop_buff10 = sum(hosp_rows$pop_buff10), pop_buff30 = sum(hosp_rows$pop_buff30), pop_buff50 = sum(hosp_rows$pop_buff50))

tab_nums(name = "tab-hosp", caption = "**Sentinel hospital catchment areas.**", display = FALSE)
```

`r tab_nums("tab-hosp", display = "full")`

```{r, disp-tab-hosp}
knitr::kable(display_hosp_tab, format = "pandoc", booktabs = T, align = "c", row.names = FALSE, col.names = c("ID", "Pop (10km)", "Pop (30km)", "Pop (50km)"))

```

Cholera surveillance zone summaries (`r tab_nums("tab-survzones", display = "cite")`)

```{r, proc-tab-survzone}

tot_pop <- sum(values(pop_rast), na.rm = TRUE)

display_survzone_tab <- data.frame(buffer = c(10, 30, 50), 
                      pop_buffer = c(buff10_mp$pop, buff30_mp$pop, buff50_mp$pop)) %>%
                      dplyr::mutate(prop_buffer = pop_buffer/tot_pop)


tab_nums(name = "tab-survzone", caption = "**Cholera surveillance zone summary.**", display = FALSE)
```

`r tab_nums("tab-survzone", display = "full")`

```{r, disp-tab-survzones}
knitr::kable(display_survzone_tab, format = "pandoc", booktabs = T, align = "c", row.names = FALSE, col.names = c("Buffer (km)", "Pop", "Prop of Pop"))

```



## To do
* Add the buffer maps
* x-axis buffer size (0-60 km in 5 km increments), y-axis percentage of population captured.
* loop through all potential buffer sizes
* High risk infection areas by cases and relative risk